\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-04-09 papers/methods/paper.tex
Responding to more of Bobs feedback

For both high-redshift and low-redshift (LowZ) data we draw from an underlying $M_B$, $x_1$, $c$ population and translate into apparent magnitude space using $\Omega_m = 0.3$, $\alpha= 0.14$ and $\beta = 3.1$. Mass probabilities are randomly drawn from the interval 0 to 1, and a mass correction with $\delta(0) = 0.08$ and $\delta(0)/\delta(\infty) =0.5$ included. Absolute magnitudes are drawn from $\mathcal{N}(-19.3, 0.1)$, true stretch values are drawn from $\mathcal{N}(0, 1)$ and true colour values are drawn from $\mathcal{N}^{\rm Skew}(0, 0.1, 2)$. Redshifts are drawn from a power law to increase the number of events as redshift increases.

Independent observational errors of $0.04$, $0.2$, $0.03$ on $m_B$, $x_1$ and $c$ (following the mean uncertainty for DES SNANA simulations) are added to create the observables. Extra dispersion of $0.02(1+3z)$ is added in quadrature to the $c$ uncertainty to simulate unexplained colour dispersion from chromatic variation in supernovae. The selection functions (a skew normal for low-redshift and an error function for high-redshift) are given independent uncertainty of $0.01$ on all parameters. The results are then passed through the selection effects, where each supernova is only selected based on $P(S|m_B)$, using a skew normal function for the LowZ supernovae and error function for the DES-like supernovae. We draw from each survey simulation until we have 1000 LowZ supernovae and 1000 DES-like supernovae, representing a statistical sample of greater power than the estimated 350 supernovae for the DES spectroscopic analysis. Sample data for 1000 high and low redshift supernovae are shown in Figure \ref{fig:simple_pop}, confirming the presence of strong selection effects in both toy surveys, as designed.

>>>>

For supernova independent uncertainty, the selection functions (a skew normal for low-redshift and an error function for high-redshift) are given independent uncertainty of $0.01$ on all parameters. We draw from each survey simulation until we have 1000 LowZ supernovae and 1000 DES-like supernovae, representing a statistical sample of greater power than the estimated 350 supernovae for the DES spectroscopic analysis. Sample data for 1000 high and low redshift supernovae are shown in Figure \ref{fig:simple_pop}, confirming the presence of strong selection effects in both toy surveys, as designed.
